Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-09-28 Paper/intro.tex
..

Time evolution of a chemically reacting system is largely dependent upon rate
constants associated with individual reactions. The rate constants are
typically assumed to exhibit a certain correlation with temperature (e.g.,
Arrhenius-type). Hence, accurate specification of the rate-controlling
parameters is critical to the fidelity of simulations. However, in practical
applications, these parameters are either specified using expert knowledge or
estimated based on a regression fit to a set of sparse and noisy
data~\cite{Burnham:1987, Burnham:1988, Vohra:2011, Sarathy:2012}.
%Consequently, the underlying uncertainty associated with the parameters and
%therefore the simulation is typically ignored. 
Intensive research efforts in recent years within the field of uncertainty quantification (UQ)
address the quantification and propagation of uncertainty in system models due to 
inadequate data, parametric uncertainty, and model errors~\cite{Vohra:2014, 
Vohra:2017, Morrison:2018, Hantouche:2018, Nannapaneni:2016, Sankararaman:2015}.

>>>>

Time evolution of a chemically reacting system is largely dependent upon rate
constants associated with individual reactions. The rate constants are
typically assumed to exhibit a certain correlation with temperature (e.g.,
Arrhenius-type). Hence, accurate specification of the rate-controlling
parameters is critical to the fidelity of simulations. However, in practical
applications, these parameters are either specified using expert knowledge or
estimated based on a regression fit to a set of sparse and noisy
data~\cite{Burnham:1987, Burnham:1988, Vohra:2011, Sarathy:2012}.
%Consequently, the underlying uncertainty associated with the parameters and
%therefore the simulation is typically ignored. 
Intensive research efforts in recent years within the field of uncertainty quantification (UQ)
address the quantification and propagation of uncertainty in system models due to 
inadequate data, parametric uncertainty, and model errors~\cite{Vohra:2014, 
Vohra:2017, Morrison:2018, Hantouche:2018, Nannapaneni:2016, Sankararaman:2015,
Reagana:2003}.
